---
title: "Assignment_V"
author: "SIVAREDDY"
date: '2022-04-14'
output: word_document
---
```{r}
library(readr)
cereals <- read_csv("C:/Users/sivap/OneDrive/Desktop/Cereals.csv")
Data_numerical <- data.frame(cereals[,4:16])

```
Libraries

```{r}
library(cluster)
library(caret)
library(dendextend)
library(factoextra)
```

Data Preprocessing. Remove all cereals with missing values. 

Removing missing values in present data

```{r}

missingvalues_removed <- na.omit(Data_numerical)

```

 Data Normalization & Data Scaling:


```{r}
Normalise <- scale(missingvalues_removed)
```
 euclidean distance to measure the distance:
 
```{r}

d <- dist(Normalise, method = "euclidean")

```
 
```{r}

##Perform Hierarchical Clustering using complete linkage.
HC <- hclust(d, method = "complete")
plot(HC)
```
```{r}
round(HC$height, 3)
```
Determining Optimal Clusters:

We can also use agnes() function to perform clustering.
Performing clustering using agnes() with single, complete, average and ward.

```{r}
HCsingle <- agnes(Normalise, method = "single")
HCcomplete <- agnes(Normalise, method = "complete")
HCaverage <- agnes(Normalise, method = "average")
HCward <- agnes(Normalise, method = "ward")

#Now we will compare the agglomerative coefficients for Single,complete, average and ward.

print(HCsingle$ac)
print(HCcomplete$ac)
print(HCaverage$ac)
print(HCward$ac)
```
The results say that the wards method is the best with the value of 0.904. Plotting the agnes using ward method and Cutting the Dendrogram. We will take k = 5 by observing the distance.

```{r}

pltree(HCward, cex = 0.6, hang = -1, main = "Dendrogram of agnes-Ward")

```

```{r}

# Hierarchical clustering using ward method.
HC1 <- hclust(d, method = "ward.D2" )

plot(HC1,cex=0.6)

plot(HCward)

rect.hclust(HCward, k=5, border = 2:10)

subgrp <- cutree(HC1, k = 5)
table(subgrp)
dataframe <- as.data.frame(cbind(Normalise,subgrp))
```
```{r}
##To visualiZe the results in scatter plot.
fviz_cluster(list(data = Normalise, cluster = subgrp))
```

Selecting the cluster that is best cereal for breakfast, which will have high protein, fiber and
low in sugar, sodium.
Choosing the Cluster of Healthy Cereals.

```{r}

Newdatacereals <- cereals
Newdatacereals_omission <- na.omit(Newdatacereals)
Clust <- cbind(Newdatacereals_omission, subgrp)
Clust[Clust$subgrp==1,]

```
```{r}
Clust[Clust$subgrp==2,]
```
```{r}
Clust[Clust$subgrp==3,]
```
```{r}
Clust[Clust$subgrp==4,]
```

```{r}
Clust[Clust$subgrp==5,]

```



Calculating mean ratings to determine the best cluster.
```{r}

mean(Clust[Clust$subgrp==1,"rating"])


```


```{r}
mean(Clust[Clust$subgrp==2,"rating"])

```

```{r}
mean(Clust[Clust$subgrp==3,"rating"])

```
```{r}
mean(Clust[Clust$subgrp==4,"rating"])

```
```{r}
mean(Clust[Clust$subgrp==5,"rating"])

```



As we can see that the mean ratings for the subgrp==1 is the highest(73.84), it’s the best
option to choose cluster 1 and the cereals in the cluster 1 for healthy diet.