---
title: "Assignment2"
author: "SivaReddy"
date: "2/20/2022"
output: pdf_document
---

# colnames are arranged according CSV file 




```{r}

library(readr)
library(caret)
library(class)
universalbank <- read_csv("universalbank.csv")

colnames(universalbank)<-c('ID', 'Age','Experience','Income','ZIP Code','Family','CCAvg','Education','Mortgage','Personal.Loan','Securities.Account','CD.Account','Online','CreditCard')
summary(universalbank)
```



```{r}

universalbank$ID <-NULL
universalbank$`ZIP Code` <-NULL

universalbank$`Personal.Loan`= as.factor(universalbank$`Personal.Loan`)


summary(universalbank)
```
#need to remove variables which are not included in the model with help of NUll Function.we should also transform character attributes to factors

```{r}

Norm_model <- preProcess(universalbank, method = c("center", "scale"))

universalbank_norm=predict(Norm_model,universalbank)
summary(universalbank_norm)

universalbank_norm$Personal.Loan = universalbank$Personal.Loan
```

#before running the model we should normalise the whole data here we used the z statistics 
#Question 1 
#we have used KNN algoritham we are anble to get value as a zero

```{r}
Train_Index = createDataPartition(universalbank$Personal.Loan,p=0.6, list=FALSE)
Train.df=universalbank_norm[Train_Index,]
Validation.df=universalbank_norm[-Train_Index,] 
To_Predict=data.frame(Age = 40, Experience = 10, Income = 84, Family = 2, CCAvg = 2, Education= 1,Mortgage = 0, Securities.Account = 0, CD.Account = 0, Online = 1,CreditCard = 1)

print(To_Predict)

To_Predict_norm<-predict(Norm_model,To_Predict)

print(To_Predict_norm)

Prediction <-knn(train=Train.df[,1:7,9:12], 
                 test=To_Predict_norm[,1:7,9:12],
                 cl=Train.df$Personal.Loan,
                 k=1)

print(Prediction)

```
#Question 2
#k=1 got highest accuracy of 0.953

```{r}
fitControl <- trainControl(method = "repeatedcv",
                           number = 3,
                           repeats = 2)
searchGrid=expand.grid(k = 1:10)

Knn.model=train(Personal.Loan~., 
                data=Train.df,
                method='knn',
                tuneGrid=searchGrid,
                trControl = fitControl,)
Knn.model

```
#Question3
#Accuarcy recoded as 0.958

```{r}
predictions<-predict(Knn.model,Validation.df)
confusionMatrix(predictions,Validation.df$Personal.Loan)

```
#Question4

```{r}
To_Predict=data.frame(Age=40,Experience = 10, Income = 84, Family = 2, CCAvg = 2, Education = 0, Mortgage = 0, Securities.Account = 0, CD.Account = 0, Online = 1, CreditCard = 1)

To_Predict_norm=predict(Norm_model,To_Predict)
predict(Knn.model,To_Predict_norm)

```
#Question5 
```{r}
splitSample <- sample(1:3, size=nrow(universalbank_norm), prob=c(0.5,0.3,0.2), replace = TRUE)

train_Data <- universalbank_norm[splitSample==1,]
valid_Data <- universalbank_norm[splitSample==2,]
test_Data <- universalbank_norm[splitSample==3,]

Predict=data.frame(Age = 40, Experience = 10, Income = 84, Family = 2, CCAvg = 2, Education= 1,Mortgage = 0, Securities.Account = 0, CD.Account = 0, Online = 1,CreditCard = 1)

print(Predict)

Predict_norm<-predict(Norm_model,Predict)

print(Predict_norm)

Prediction_newsplit <-knn(train=Train.df[,1:7,9:12], 
                          test=To_Predict_norm[,1:7,9:12],
                          cl=Train.df$Personal.Loan,
                          k=1)

print(Prediction_newsplit)

fitControl2 <- trainControl(method = "repeatedcv",
                            number = 3,
                            repeats = 2)
searchGrid=expand.grid(k = 1:10)

Knn.model2 =train(Personal.Loan~., 
                  data=Train.df,
                  method='knn',
                  tuneGrid=searchGrid,
                  trControl = fitControl2,)
Knn.model2

predictions2<-predict(Knn.model2,Validation.df)
confusionMatrix(predictions2,Validation.df$Personal.Loan)

```


